Mountaineering: Be lucky first, prepared second

### 2024-12-04 paper/paper.qmd
update paper

---
title: "Mountaineering: Be lucky first, prepared second"
subtitle: "Preperation and Timing are more important than Gender Identity, Age, Amount of expedition members, and height of peak when mountaineering in the Himalayas."
author: 
  - Daniel Xu
thanks: "Code and data are available at: [https://github.com/possibleburger2/](https://github.com/possibleburger2/Himalayan-Climbing-Expeditions-Data-Analysis)."
date: today
date-format: long
abstract: "This study asseses factors that contribute to success in Himalayan Expeditions from Himalayan Expedition data from 1905-2019"
format: pdf
number-sections: true
bibliography: references.bib

@@

## Climbing success relys on oxygen used signifigantly

>>>>

---
title: "Mountaineering: Be lucky first, prepared second"
subtitle: "Preperation and Timing are more important than Gender Identity, Age, Amount of expedition members, and height of peak when mountaineering in the Himalayas."
author: 
  - Daniel Xu
thanks: "Code and data are available at: [https://github.com/possibleburger2/](https://github.com/possibleburger2/Himalayan-Climbing-Expeditions-Data-Analysis)."
date: today
date-format: long
abstract: "This study analyzes over a century of Himalayan mountaineering expeditions (1905–2019) to identify key factors influencing success. Using logistic regression, we find that preparation and timing—such as the use of supplemental oxygen and climbing during optimal seasons—are more important predictors of success than individual traits like age, gender, or the height of the peak. These findings reveal that success in high-altitude climbing depends more on strategic choices than personal attributes. This insight underscores the value of informed planning and environmental awareness for achieving mountaineering goals."
format: pdf
number-sections: true
bibliography: references.bib

@@

## Climbing success relys on oxygen used significantly
